### 2023-02-10 article.tex
Use abstract*
Remove subsubsubsection
Use begin and end for abstact
Use begin and end for abstact (no asterisk)
Check for 'svmult.cls'
Improved title

\setcounter{chapter}{7}
\chapter{Research code is paradata and as vital as the article itself}

\abstract{

Paradata is data about the data collection process,
that allows use and reuse of data.
Within the context of computational research,
computer code is the paradata of an experiment,
allowing the study to be reproduced.
A recent study recommended how to make paradata (more) useful,
for paradata in general.
This study applies those recommendations to computer code,
using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.

} % abstract

@@

\subsubsubsection{Assessment of code}

\subsubsubsection{Extending code}

>>>>

\setcounter{chapter}{7}
\chapter{How to make research code useful paradata}

\abstract*{
Paradata is data about the data collection process,
that allows use and reuse of data.
Within the context of computational research,
computer code is the paradata of an experiment,
allowing the study to be reproduced.
A recent study recommended how to make paradata (more) useful,
for paradata in general.
This study applies those recommendations to computer code,
using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.
} % abstract

@@
